Appendix

### 2020-03-04 manuscript/appendix.Rmd
annotate equations on scatter plot

# fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
# fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`, 
#                           tn_pred = fit_tn$fitted.values, 
#                           stringsAsFactors = FALSE)
# ggplot(data = fit_tn_pred) + 
#   geom_point(aes(x = tn, y = tn_pred)) +
#   geom_abline(slope = 1)
# 
# fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
# fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`, 
#                           tp_pred = fit_tp$fitted.values, 
#                           stringsAsFactors = FALSE)
# ggplot(data = fit_tp_pred) + 
#   geom_point(aes(x = tp, y = tp_pred)) +
#   geom_abline(slope = 1)

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  ylab("log(TN) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
  ylab("log(TP) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10()
)

>>>>

fit_tn      <- lm(log(tn) ~ log(ag), data = dt)
fit_tn_pred <- data.frame(tn = fit_tn$model$`log(tn)`,
                          tn_pred = fit_tn$fitted.values,
                          ag = fit_tn$model$`log(ag)`,
                          stringsAsFactors = FALSE)
# ggplot(data = fit_tn_pred) + 
#   geom_point(aes(x = tn, y = tn_pred)) +
#   geom_abline(slope = 1)
# 
fit_tp      <- lm(log(tp) ~ log(ag), data = dt)
fit_tp_pred <- data.frame(tp = fit_tp$model$`log(tp)`,
                          tp_pred = fit_tp$fitted.values,
                          ag = fit_tp$model$`log(ag)`,
                          stringsAsFactors = FALSE)
# ggplot(data = fit_tp_pred) + 
#   geom_point(aes(x = tp, y = tp_pred)) +
#   geom_abline(slope = 1)

get_formula <- function(response_var, model){
  # https://stackoverflow.com/a/26640226/3362993
  res <- as.formula(
    paste0(response_var, " ~ ", round(coefficients(model)[1],2), "", 
      paste(sprintf(" %+.2f*%s ", 
                    coefficients(model)[-1],  
                    names(coefficients(model)[-1])), 
            collapse="")
    )
  )
  paste(res[2], res[3], sep=' ~ ')
}

cowplot::plot_grid(
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tn)) + 
  geom_line(data = fit_tn_pred, aes(x = exp(ag), y = exp(tn_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 12000, label = get_formula("log(tn)", fit_tn), 
           size = 2) +
  ylab("log(TN) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot(), 
ggplot(data = dt) + 
  geom_point(aes(x = ag, y = tp)) + 
    geom_line(data = fit_tp_pred, aes(x = exp(ag), y = exp(tp_pred)), 
             color = "red") +
  annotate("text", x = 14, y = 900, label = get_formula("log(tp)", fit_tp), 
           size = 2) +
  ylab("log(TP) (ug/L)") +
  xlab("log(Percent Agriculture)") +
  scale_x_log10() + scale_y_log10() +
  theme_cowplot()
)
